Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-10-04 ms.tex
Updates from Overleaf

\begin{figure}[ht!]
%\includegraphics{}  % preferably .eps
\caption{Example of satellite avoidance maps. \label{fig-simulated-scheduler}}
\end{figure}

As shown in Figure \ref{fig-simulated-scheduler}, the predicted OneWeb constellation map has more negative reward
weighting than other constellations. Although the OneWeb constellation has fewer satellites than
the StarlinkV2 constellation, the OneWeb constellation is at a higher altitude, meaning that its
satellites will be illuminated for a longer portion of the night, and not just close to twilight.
Therefore, OneWeb shows more negative weighting than StarlinkV2 though it has a smaller
satellite population.
To investigate whether the scheduler behaves how we expect with the new satellite
weighting added we create a testing function that measures the length of satellite streaks in the
simulated field of views. To ensure efficiency, only satellites that are above the altitude limit and
illuminated by the sun will be considered. Satellites below the altitude limit (indicated in the gray
region in Figure \ref{fig-simulated-scheduler}) can’t be observed in pointings and are therefore not included for efficiency.
For each satellite, we first determine whether they are in the field of view for any given
telescope pointing by calculating their distance from the center of the field of view. If their
distance from the field of view is less than the radius of the field of view, the satellite has crossed
through the pointing. To quantify the impact of the satellite on the pointing, we then project the satellite location as well as the pointing to a 2D x,y plane. In the 2D plane, the field of pointing
becomes roughly a circle and the start and end locations of the satellite become two points on the
plane. Using the shapely python library, we calculate the intersection length of the satellite location
points and the circle.
Therefore, with a given simulated satellite constellation and a schedule of observations,
we record the number of satellites that occur in each field of view and measure how long the
satellite streaks are. Using a realistic estimated satellite streak width of 50 pixels, we can convert
the streak length results into the number of affected image pixels, which allows us to
quantitatively measure the efficiency of the dodging algorithm with pixel loss.

>>>>

\begin{figure}[ht!]
% \plotone{plots/}
\caption{Example of satellite avoidance maps. \label{fig-simulated-scheduler}}
\end{figure}

As shown in Figure \ref{fig-simulated-scheduler}, the predicted OneWeb constellation map has more negative reward
weighting than other constellations. Although the OneWeb constellation has fewer satellites than
the StarlinkV2 constellation, the OneWeb constellation is at a higher altitude, meaning that its
satellites will be illuminated for a longer portion of the night, and not just close to twilight.
Therefore, OneWeb shows more negative weighting than StarlinkV2 though it has a smaller
satellite population.
To investigate whether the scheduler behaves how we expect with the new satellite
weighting added we create a testing function that measures the length of satellite streaks in the
simulated field of views. To ensure efficiency, only satellites that are above the altitude limit and
illuminated by the sun will be considered. Satellites below the altitude limit (indicated in the gray
region in Figure \ref{fig-simulated-scheduler}) can’t be observed in pointings and are therefore not included for efficiency.
For each satellite, we first determine whether they are in the field of view for any given
telescope pointing by calculating their distance from the center of the field of view. If their
distance from the field of view is less than the radius of the field of view, the satellite has crossed
through the pointing. To quantify the impact of the satellite on the pointing, we then project the satellite location as well as the pointing to a 2D x,y plane. In the 2D plane, the field of pointing
becomes roughly a circle and the start and end locations of the satellite become two points on the
plane. Using the shapely python library, we calculate the intersection length of the satellite location
points and the circle.
Therefore, with a given simulated satellite constellation and a schedule of observations,
we record the number of satellites that occur in each field of view and measure how long the
satellite streaks are. Using a realistic estimated satellite streak width of 50 pixels ($\sim$XXX arcsec), we can convert
the streak length results into the number of affected image pixels, which allows us to
quantitatively measure the efficiency of the dodging algorithm with pixel loss.

XXX--Should we add in the results from looking at a run with twilight NEO survey observations? Doesn't flow well with everything else, but I think it is a result that will help some folks calm down a bit that we aren't going to miss tons of killer asteroids even with large constellations.
